Notes on conformal manifolds

### 2025-09-22 Draft_MLFlatDirections.tex
Fixed a couple of typos

\begin{abstract}
	We investigate the structure of conformal manifolds around AdS$_3 \times S^3$ which lift from continuous flat directions in the scalar potential of gauged supergravity resulting from six-dimensional $\mathcal{N}=(1,1)$.
	Our approach combines numerical exploration and symbolic inference. For the latter, we develop a symbolic regression algorithm based on Sequential Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces. 
	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
\end{abstract}

@@

		Sequential importance sampling \cite{...} further assumes that the density functions $\pi_n(z)$ can be given in terms of importance densities $q^k_n(z)$ and weights $w^k_n$ as $\pi_n(z) = \sum w^k_n q^k_n(z)/Z_n$, and these importance densities can be sequentially given as
		 \begin{equation}
		 	q_n(z_n) = q_{n-1}(z_{n-1}) q_{n\vert n-1}(z_n\vert z_{n-1})\,.
		 \end{equation}
At each epoch, we $\pi_{n}$ can be approximated via a set of particles and weights $\{z_{n}^k,\ w_{n}^k\}$  so that\footnote{In the following, we always normalise the weights so that $\sum_k w_{n}^k=1$.}
		 \begin{equation}
		 	\pi_n(z) \approx \sum_k w_{n}^k\ \delta(z-z_{n}^k)\,,
		 \end{equation}
To obtain a new set $\{z_{n+1}^k,\ w_{n+1}^k\}$ approximating $\pi_{n+1}$, we sample from the forward propagation kernel $q_{n+1}(z_{n+1}\vert z_n)$ that defines how we generate the state at time $n+1$ given the state at time $n$.
Similarly, the evolution of the weights is given by
\[
	w_{n+1} = \frac{\gamma_{n+1}}{q_{n+1}} = \frac{\gamma_{n+1}}{q_{n}\ q_{n+1 \vert n}} = w_{n}\ \alpha_{n+1}\,,
\]
where the incremental importance weights $\alpha_{n}^k$ are given by
		\begin{equation}	\label{eq: incremental_importance}
			\begin{aligned}
				\alpha^k_{n+1} &= \frac{\gamma_{n+1}(z_{n+1})}{\gamma_{n}(z_n)}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}	\\
				&=e^{-\beta_nL(z_n)+\beta_{n+1}L(z_{n+1})}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}\,.
			\end{aligned}
		\end{equation}

		For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm. 
On every step, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
The moves that have been allowed in our implementation are:
		\begin{itemize}
			\item \textbf{Coefficient pertubation}. Given a polynomial $z_{n}$, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$. E.g.
			\[
				2 x_1 + 3 x_2^2 \mapsto  2.1 x_1 + 3 x_2^2\,.
			\]
			\item \textbf{Variable multiplication}. Given a polynomial $z_{n}$, we pick randomly one of its monomials, and multiply it by one of the available variables. E.g.
			\[
				2 x_1 + 3 x_2^2 \mapsto  2 x_1 x_2 + 3 x_2^2\,.
			\]
			\item \textbf{Variable division}. Given a polynomial $z_{n}$, we choose randomly one of its monomials, and divide it by one of its variables. E.g.
			\[
				2 x_1 x_2 + 3 x_2^2 \mapsto  2 x_1 + 3 x_2^2\,.
			\]
		\end{itemize}
		Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
%		For the case of coefficient perturbations, the transition is symmetric. 
%		However, this symmetry does not hold in general. For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \). In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
After performing these updates, the change is accepted based on the temperature-dependent rate
		\begin{equation}\label{eq:acceptanceratio}
			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)\,.
		\end{equation}
		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
		The kernels $q$ and $\tilde{q}$ thus encapsulate the effects of performing these operations on the polynomials at step $n$.

>>>>

\begin{abstract}
	We investigate the structure of conformal manifolds around AdS$_3 \times S^3$ which lift from continuous flat directions in the scalar potential of gauged supergravity resulting from six-dimensional $\mathcal{N}=(1,1)$.
	Our approach combines numerical exploration and symbolic inference. For the latter, we develop a symbolic regression algorithm based on Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces. 
	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
\end{abstract}

@@

		Sequential importance sampling \cite{...} further assumes that the density functions $\pi_n(z)$ can be given in terms of importance densities $q^k_n(z)$ and weights $w^k_n$ as $\pi_n(z) = \sum w^k_n q^k_n(z)/Z_n$, and these importance densities can be sequentially given as
		 \begin{equation}
		 	q_n(z_n) = q_{n-1}(z_{n-1}) q_{n\vert n-1}(z_n\vert z_{n-1})\,.
		 \end{equation}
At each epoch, we $\pi_{n}$ can be approximated via a set of particles and weights $\{z_{n}^k,\ w_{n}^k\}$  so that\footnote{In the following, we always normalise the weights so that $\sum_k w_{n}^k=1$.}
		 \begin{equation}
		 	\pi_n(z) \approx \sum_k w_{n}^k\ \delta(z-z_{n}^k)\,,
		 \end{equation}
To obtain a new set $\{z_{n+1}^k,\ w_{n+1}^k\}$ approximating $\pi_{n+1}$, we sample from the forward propagation kernel $q_{n+1}(z_{n+1}\vert z_n)$ that defines how we generate the state at time $n+1$ given the state at time $n$.
Similarly, the evolution of the weights is given by \gl{for $k>1$, this is a bit schematic...}
\[
	w_{n+1} = \frac{\gamma_{n+1}}{q_{n+1}} = \frac{\gamma_{n+1}}{q_{n}\ q_{n+1 \vert n}} = w_{n}\ \alpha_{n+1}\,,
\]
where the incremental importance weights $\alpha_{n}^k$ are given by
		\begin{equation}	\label{eq: incremental_importance}
			\begin{aligned}
				\alpha^k_{n+1} &= \frac{\gamma_{n+1}(z_{n+1})}{\gamma_{n}(z_n)}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}	\\
				&=e^{-\beta_nL(z_n)+\beta_{n+1}L(z_{n+1})}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}\,.
			\end{aligned}
		\end{equation}

		For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm. 
On every step, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
The moves that have been allowed in our implementation are:
		\begin{itemize}
			\item \textbf{Coefficient pertubation}. Given a polynomial $z_{n}$, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$. E.g.
			\[
				2 x_1 + 3 x_2^2 \mapsto  2.1 x_1 + 3 x_2^2\,.
			\]
			\item \textbf{Variable multiplication}. Given a polynomial $z_{n}$, we pick randomly one of its monomials, and multiply it by one of the available variables. E.g.
			\[
				2 x_1 + 3 x_2^2 \mapsto  2 x_1 x_2 + 3 x_2^2\,.
			\]
			\item \textbf{Variable division}. Given a polynomial $z_{n}$, we choose randomly one of its monomials, and divide it by one of its variables. E.g.
			\[
				2 x_1 x_2 + 3 x_2^2 \mapsto  2 x_1 + 3 x_2^2\,.
			\]
		\end{itemize}
		Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
%		For the case of coefficient perturbations, the transition is symmetric. 
%		However, this symmetry does not hold in general. For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \). In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
After performing these updates, the change is accepted based on the temperature-dependent rate \gl{need to double check this}
		\begin{equation}\label{eq:acceptanceratio}
			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)\,.
		\end{equation}
		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
		The kernel $q(z_{n-1}^k | z_n^k)$ thus encapsulates the effects of performing these operations on the polynomials at step $n$.
